In this thesis, we have proposed a state-of-the-art topic model, Transformer Embedded Correlated Topic Model(TECTM), and with its extension for time-series data, Dynamic Transformer Embedded Correlated Topic Model(DTECTM). The result has shown TECTM a better performance in returning high quality topics compared with other state-of-the-art models. Our model also demonstrates a capability in classifying substantial number of topics.

% Time-series
We also expanded the model to handle time-series data. The model was integrated with Gaussian process latent variable model, which make able the model to capture the time-series information from document set. We also expose our model has a competitive performance compared to other state of the art models.

% Limitations
In the studies though our thesis, we carried a series of experiments with varies of metrics to validate the models. Yet our model is capable to obtain a high quality topics in terms of topic coherence and topic diversity. However, we still notice that DTECTM model does not produce a good enough perplexity score compared with other models. So it is expected to improve the predictivity of the model as a future work.

% Future works
Their are more improvement to the models. First, Nonparametric Bayesian method did not consider in the research due to the time limitation. Also, since graph model and document shares similarity on power law, we expect to explore the possibility to use graph machine learning knowledge to work with the model.